DataCamp: An Interactive Teaching Tool

### 2018-01-04 manuscript.tex
edit manuscript

\subsection{Interactive tools to learn R}
With this increased use of R in classrooms, an effective tool to familiarize students with statistical software is needed
\citep{Baumer2014}. While R software provides users with extraordinary statistical capabilities, there is certainly a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including \textit{swirl} \citep{Kross} and Try R \citep{TryR}. 
Interactive tools allow students to work through coding problems while receiving immediate feedback and can be used in and outside of the classroom.

>>>>

\subsection{Interactive tools to learn R}
With the increased use of R in classrooms, an effective tool to familiarize students with statistical software is needed
\citep{Baumer2014}. While R software provides users with extraordinary statistical capabilities, there is certainly a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including \textit{swirl} \citep{Kross} and Try R \citep{TryR}. 
Interactive tools allow students to actively work through coding problems while receiving immediate feedback.
